A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-18 doc/large_strain.tex
Improve description of sum factorization

and this is the same as for a regular matrix-vector product where the entries are already precomputed. Assuming tensor product ansatz spaces and a tensor product quadrature rule, evaluation of this operations can be performed more efficiently.

@@

Therefore the result of application of the scalar-valued mass operator, represented as a vector $y_i$, on a single element $K$ can be written as

@@

{\color{red} Daniel: please adjust the discussion above, I think we need to add more on what happens with those 4 loops}
In general, this reordering reduces the arithmetic complexity to $\mathcal{O}(dn^{d+1})$ and is called sum factorization.

>>>>

and this is the same as for a regular matrix-vector product where the entries are already precomputed. Assuming tensor product ansatz spaces and a tensor product quadrature rule, evaluation of this operations can be performed more efficiently using a technique called ``sum factorization''.

@@

Therefore, the result of application of the scalar-valued mass operator, represented as a vector $y_i$, on a single element $K$ can be written as

@@

These four loops all have the same structure. We either keep the shape function fixed and iterate over the quadrature points in one spatial direction (in the first two sums) or keep the quadrature point and fixed and iterate over all the shape functions in one spatial direction (in the last two sums). Since each of these $2\cdot d$ loops has a complexity of $n$ and we perform them for $n^d$ values in quadrature points or values in degrees of freedoms simultaneously, we end up with an arithmetic complexity of $\mathcal{O}(dn^{d+1})$.
